A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
ordering of results in overall table.

It is also important to verify some correlations between variables. To that
matter, we've tested some apparent situations, such as the influence of the age,
hours of work per week and educational level on the amount gained by an
individual. The figures \ref{fig:age_plus50}, \ref{fig:education_plus50} and
\ref{fig:hpw_plus50} show that there is a tendency for older people, people with
a higher educational level and people who work a great amount of hours per week
to gain a larger amount of money.

@@

\begin{table}
    \begin{center}
    \begin{tabular}{ | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error rate} \\ \hline
    CN2 & 15.20 \\ \hline
    ID3 & 15.68 \\ \hline
    ADTree & 18.49 \\ \hline
    ILP (Aleph) & 20.45 \\ \hline
    Bayesian Networks (Simulated Annealing) & 21.09 \\ \hline
    C4.5 & 18.84 \\ \hline
    Random Forest & 22.71 \\ \hline
    Bayesian Networks (Hill Climbing) & 22.93 \\ \hline
    CART & 25.37 \\ \hline
    Bayesian Networks (Genetic Search) & - \\ \hline
    \end{tabular}
    \caption{Error rates for the different algorithms used in the classification process}
    \label{tbl:overall_results}
    \end{center}
\end{table}

>>>>

It is also important to verify some relations between variables. To that
matter, we've tested some apparent situations, such as the influence of the age,
hours of work per week and educational level on the amount gained by an
individual. The figures \ref{fig:age_plus50}, \ref{fig:education_plus50} and
\ref{fig:hpw_plus50} show that there is a tendency for older people, people with
a higher educational level and people who work a great amount of hours per week
to gain a larger amount of money.

@@

\begin{table}
    \begin{center}
    \begin{tabular}{ | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error rate} \\ \hline
    CN2 & 15.20 \\ \hline
    ID3 & 15.68 \\ \hline
    ADTree & 18.49 \\ \hline
    C4.5 & 18.84 \\ \hline
    Bayesian Networks (Simulated Annealing) & 19.15 \\ \hline
    Bayesian Networks (Hill Climbing) & 20.03 \\ \hline
    ILP (Aleph) & 20.45 \\ \hline
    Random Forest & 21.01 \\ \hline
    Bayesian Networks (Genetic Search) & 21.26 \\ \hline
    CART & 21.34 \\ \hline
    \end{tabular}
    \caption{Error rates for the different algorithms used in the classification process}
    \label{tbl:overall_results}
    \end{center}
\end{table}
